---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(and)
# remotes::install_github("GuangchuangYu/badger")
library(badger)
```

# and

<!-- badges: start -->
<!-- `r badge_cran_release(color = "brightgreen")` -->
`r badge_lifecycle("experimental")`
`r badge_license(color = "blueviolet")`
<!-- `r badge_github_actions(action = "R-CMD-check")` -->
<!-- `r badge_codecov()` -->
<!-- `r badge_dependencies()` -->
<!-- badges: end -->

**and** constructs language-aware lists in R. It extends the functionality of functions like `knitr::combine_words()` and `glue::glue_collapse()` to make "and"-separated and "or"-separated lists that automatically conform to the user's R language settings.

## Installation

<!-- You can install the released version of **nombre** from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` {r eval = FALSE} -->
<!-- install.packages("nombre") -->
<!-- ``` -->

You can install the development version of **and** from GitHub with:

``` {r eval = FALSE}
# install.packages("pak")
pak::pkg_install("rossellhayes/and")
```

## Usage

```{r include = FALSE}
library(and)
```

`and()` creates "and"-separated lists from vectors.

```{r}
names <- c("John", "Paul", "George", "Ringo")
and(names)
```

But the Oxford comma is less common in other varieties of English, what happens if I change my R language to British English?

```{r}
Sys.setenv(LANG = "en_GB")
and(names)
```

What about other languages?

```{r}
Sys.setenv(LANG = "es")
and(names)
Sys.setenv(LANG = "fr")
and(names)
Sys.setenv(LANG = "eu")
and(names)
```

### Handling the nuances

Creating a list is not as simple as putting a different word between the last two items.
For example, in Spanish and Italian, the word for "and" changes depending on the first letter of the next word:

```{r}
princess_bride <- c("Wesley", "Fezzik", "Iñigo Montoya")
Sys.setenv(LANG = "es")
and(princess_bride)
Sys.setenv(LANG = "it")
and(princess_bride)

the_boss <- c("Bruce Springsteen", "E Street Band")
Sys.setenv(LANG = "es")
and(the_boss)
Sys.setenv(LANG = "it")
and(the_boss)
```

### "or"-separated lists

Everything `and()` can do `or()` can do better. Just use `or()` to create "or"-separated lists with all the same contextual awareness.

```{r}
outcomes <- c("win", "lose", "draw")
Sys.setenv(LANG = "en_US")
or(outcomes)
Sys.setenv(LANG = "es")
or(outcomes)
```

### Hardcoding language

Don't want the language of you string to depend on the user's environment variables?
You can explicitly set the language using the `lang` argument.

```{r}
and(names, lang = "en_US")
and(names, lang = "en_GB")
and(names, lang = "es")
and(names, lang = "fr")
```

---

Please note that **nombre** is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
